`r params$project_title`

### 2020-11-27 reports/rmarkdown/01_data_pre_processing.Rmd
updates integrated report

```{r, echo = FALSE}
library(igraph)
library(rafalib)
library(sva)
library(batchelor)
source("~/repos/niceRplots/R/plotting_functions.R")
source("~/repos/niceRplots/R/add_fig_label.R")
source("~/repos/niceRplots/R/helper_functions.R")

@@

#color palettes
pal <- RColorBrewer::brewer.pal(8,"Set1") #color pallete for plots
heat_pal <- c("#000000", colorRampPalette(c("#000000","grey5","grey30","orange3","yellow","yellow","white"))(90))
cor_pal <- colorRampPalette(c("navy","white","firebrick"))(90)
```

@@

# Transform phyloseq data into normalized matricies ( log2[CP1K] )
# datasets <- lapply(datasets,function(x){
#     x <- t(log2( t(x) / colSums(x) * 1000 + 1))
# })
# lapply(datasets,dim)
```

>>>>

```{r, echo = FALSE}
library(igraph)
library(rafalib)
library(sva)
library(batchelor)
remotes::install_github("czarnewski/niceRplots",upgrade = "always",force = T)
library(niceRplots)

@@

#color palettes
pal <- c(RColorBrewer::brewer.pal(9,"Set1"),RColorBrewer::brewer.pal(8,"Set2"),
         RColorBrewer::brewer.pal(9,"Pastel1"),RColorBrewer::brewer.pal(8,"Pastel2")) #color pallete for plots
heat_pal <- c("#000000", colorRampPalette(c("#000000","grey5","grey30","orange3","yellow","yellow","white"))(90))
cor_pal <- colorRampPalette(c("navy","white","firebrick"))(90)
```

@@

# Transform phyloseq data into normalized matricies ( log2[CP1K] )
# datasets <- lapply(datasets,function(x){
#     x <- t(log2( t(x) / colSums(x) * 1000 + 1))
# })
# lapply(datasets,dim)

# Extract taxonomic information to file
taxa_info <- lapply(dataset_names, function(x){
  x <- read.csv( paste0(PATH,"/",x))
  temp <- as.matrix(x[,c((ncol(x)-6):ncol(x))])
  temp[is.na(temp)] <- "NA"
  return(t(temp))
})
taxa_info <- t(as.data.frame(taxa_info))
rownames(taxa_info) <- sub("other.","other ",rownames(taxa_info))
rownames(taxa_info) <- sub("[.][0123456789","other ",rownames(taxa_info))
sps <- apply( taxa_info[,6:7] ,1,function(x) paste(x,collapse ="_"))
not_complete <- grepl("_NA",sps)
taxa <- apply( taxa_info ,1,function(x) paste(x,collapse ="_"))
taxa[not_complete] <- sub("_NA.*","",taxa[not_complete])
taxa[not_complete] <- sub(".*_","other ",taxa[not_complete])
taxa[!not_complete] <- sps[!not_complete]
taxa <- sub("_"," ",taxa)
use <- !is.na(taxa) & (taxa != "NA")
taxa[taxa == "NA"] <- "other"
rownames(taxa_info) <- taxa
taxa_info <- taxa_info[! duplicated(rownames(taxa_info)),]
write.csv2(taxa_info, paste0(PATH,"../results/taxonomy.csv"),row.names = T)
```

### 2020-11-27 reports/rmarkdown/02_individual_reports.Rmd
updates integrated report

#color palettes
pal <- c(RColorBrewer::brewer.pal(9,"Set1"),RColorBrewer::brewer.pal(8,"Set2")) #color pallete for plots
heat_pal <- c("#000000", colorRampPalette(c("#000000","grey5","grey30","orange3","yellow","yellow","white"))(90))
cor_pal <- colorRampPalette(c("navy","white","firebrick"))(90)

>>>>

#color palettes
pal <- c(RColorBrewer::brewer.pal(9,"Set1"),RColorBrewer::brewer.pal(8,"Set2"),
         RColorBrewer::brewer.pal(9,"Pastel1"),RColorBrewer::brewer.pal(8,"Pastel2")) #color pallete for plots
heat_pal <- c("#000000", colorRampPalette(c("#000000","grey5","grey30","orange3","yellow","yellow","white"))(90))
cor_pal <- colorRampPalette(c("navy","white","firebrick"))(90)
